\sysfull

### 2018-04-17 paper/evaluation.tex
eval: downscaling -> downsizing

Our evaluation quantitavely demonstrates that \sys (i) \emph{reduces the memory
protection overhead} by coalescing, (ii) \emph{improves execution speed} for
conservative static task decompostions compared to state-of-the-art runtimes; %
and (iii) \emph{provides computation progress} at the sub-task granularity,
preventing non-termination at adverse energy conditions where state-of-the-art
runtimes fail. We measured the execution time of the benchmarks implemented
using \sys with each variant of the two proposed adaptation mechanisms:
\emph{task coalescing} and \emph{task downscaling}. We compared \sys's best
configurations against a state-of-the art system, Alpaca~\cite{alpaca}. We have
also broken down \sys's overhead to explain the source of \sys's improved
performance.

@@

We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile time.
Figure~\ref{fig:runtime} (right) shows the average execution time of each
application for Coala and Alpaca, normalized to the latter. The results show
that \sys provides a performance benefit compared to Alpaca for most
applications, with the exception of \textbf{ar} and \textbf{cuckoo} at some
distances.  The speedup is greatest for applications with repeated write after
read dependencies throughout their code, particularly involving arrays
(\textbf{dijkstra}, \textbf{fft} and \textbf{sort}). \sys's virtualized memory
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables, including array elements, \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textbf{ar}, \textbf{cuckoo}).

The \textbf{fft} benchmark did not complete at distances larger than
15\,cm~\footnote{At distances greater than 15~cm, energy incoming during
execution is negligible and stored energy is insufficient to complete some of
the static tasks.} with neither Alpaca, nor Coala \emph{without the downscaling
mechanism}. This is marked with $\infty$ signs in Figure~\ref{fig:coalescing}
(left).  This non-terminating condition cannot be avoided in Alpaca, due to the
fixed, non-adaptive nature of its tasks.  In contrast, our next experiment
shows how \sys's task downscaling adaptation mechanism eliminates this
non-termination, without changing the static tasks and without recompiling the
application.

In a separate experiment, we have enabled task downscaling in \sys and measured
the execution time for \textbf{fft} benchmark at 60\,cm from the signal
generator antenna --- even \emph{farther} than the distance at which this
benchmark failed to terminate in the previous experiment. \sys executed the
benchmark successfully without (NC) and with coalescing (ETA). The application
took longer to complete than at a shorter distance of 15~cm in the previous
experiment, because of smaller (negligible) incoming energy at the larger
distance. The variant without coalescing (NC) slowed down by 2.16$\times$ and the
variant with ETA coalescing slowed down by 2.31$\times$ slower, but at both
distances, ETA completed faster than NC.
%
For comparison, the run time with Alpaca is effectively infinite at this
distance, which is a consequence of its non-adaptive static tasks.

>>>>

Our evaluation quantitavely demonstrates that \sys (i) \emph{reduces the memory
protection overhead} by coalescing, (ii) \emph{improves execution speed} for
conservative static task decompostions compared to state-of-the-art runtimes; %
and (iii) \emph{provides computation progress} at the sub-task granularity,
preventing non-termination at adverse energy conditions where state-of-the-art
runtimes fail. We measured the execution time of the benchmarks implemented
using \sys with each variant of the two proposed adaptation mechanisms:
\emph{task coalescing} and \emph{task downsizing}. We compared \sys's best
configurations against a state-of-the art system, Alpaca~\cite{alpaca}. We have
also broken down \sys's overhead to explain the source of \sys's improved
performance.

@@

We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile time.
Figure~\ref{fig:runtime} (right) shows the average execution time of each
application for \sys and Alpaca, normalized to the latter. The results show
that \sys provides a performance benefit compared to Alpaca for most
applications, with the exception of \textbf{ar} and \textbf{cuckoo} at some
distances.  The speedup is greatest for applications with repeated write after
read dependencies throughout their code, particularly involving arrays
(\textbf{dijkstra}, \textbf{fft} and \textbf{sort}). \sys's virtualized memory
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables, including array elements, \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textbf{ar}, \textbf{cuckoo}).

The \textbf{fft} benchmark did not complete at distances larger than
15\,cm~\footnote{At distances greater than 15~cm, energy incoming during
execution is negligible and stored energy is insufficient to complete some of
the static tasks.} with neither Alpaca, nor \sys \emph{without the downsizing
mechanism}. This is marked with $\infty$ signs in Figure~\ref{fig:coalescing}
(left).  This non-terminating condition cannot be avoided in Alpaca, due to the
fixed, non-adaptive nature of its tasks.  In contrast, our next experiment
shows how \sys's task downsizing adaptation mechanism eliminates this
non-termination, without changing the static tasks and without recompiling the
application.

In a separate experiment, we have enabled task downsizing in \sys and measured
the execution time for \textbf{fft} benchmark at 60\,cm from the signal
generator antenna --- even \emph{farther} than the distance at which this
benchmark failed to terminate in the previous experiment. \sys executed the
benchmark successfully without (NC) and with coalescing (ETA). The application
took longer to complete than at a shorter distance of 15~cm in the previous
experiment, because of smaller (negligible) incoming energy at the larger
distance. The variant without coalescing (NC) slowed down by 2.16$\times$ and the
variant with ETA coalescing slowed down by 2.31$\times$ slower, but at both
distances, ETA completed faster than NC.
%
For comparison, the run time with Alpaca is effectively infinite at this
distance, which is a consequence of its non-adaptive static tasks.
